Brownian Dynein Model

### 2015-10-23 latex/derivation.tex
Add one derivative to latex derivation.

We simplify...

\begin{align}
  X_{nm} &= \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\Big) \mp \sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
  Y_{nm} &= \frac{L_{s}}{L_{n}}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\sqrt{L_{n}^2-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2L}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2L}\sqrt{L_{n}^2-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}}\bigg)^2} \Bigg) \\
\end{align}

@@

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{nb} &= \frac{1}{\gamma} \Big(F_{xnb} + \lambda_{fs}(X_{nm} - X_{nb})\Big) + R_{xnb} \\
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})\Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nb} &= \frac{1}{\gamma} \Big(F_{ynb} + \lambda_{fs}(Y_{nm} - Y_{nb})\Big) + R_{ynb} \\
  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})\Big) + R_{ybr}
\end{align}

\begin{align}
  \dot{X}_{nm} &= \dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) + \frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) + \frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + R_{xt } \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xmr} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{fs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nm} &= \dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) + \frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) + \frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + R_{yt } \\
  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{fs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(X_{nm} - X_{nb}) =
\dot{X}_{nb} + \mn L_{s}\sin(\Theta_{nb})\dot{\Theta}_{nb} - R_{xml} - \frac{1}{\gamma}F_{xml} + \dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } \\
- \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr}
-\frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Ax}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{t } - X_{nm}) =
\dot{X}_{nm} + \mn L_{t}\sin(\Theta_{nm})\dot{\Theta}_{nm} - R_{xt } - \frac{1}{\gamma}F_{xt } + \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Bx}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(X_{fm} - X_{t }) =
\dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} - R_{xmr} - \frac{1}{\gamma}F_{xmr}
+ \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} - R_{xbr} - \frac{1}{\gamma}F_{xbr}
\label{eq:Cx}
\end{equation}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bs}(Y_{nm} - Y_{nb}) =
\dot{Y}_{nb} + L_{s}\cos(\Theta_{nb})\dot{\Theta}_{nb} - R_{yml} - \frac{1}{\gamma}F_{yml} + \dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} \\
- R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm}
+ \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Ay}
\end{multline}%Fix'd

\begin{multline}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{t } - Y_{nm}) =
\dot{Y}_{nm} + L_{t}\cos(\Theta_{nm})\dot{\Theta}_{nm} - R_{yt} - \frac{1}{\gamma}F_{yt } + \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
- R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} - R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:By}
\end{multline}%Fix'd

\begin{equation}
\mn\frac{1}{\gamma}\lambda_{bt}(Y_{fm} - Y_{t }) =
\dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
- R_{ybr} - \frac{1}{\gamma}F_{ybr}
\label{eq:Cy}
\end{equation}%Fix'd

>>>>

We simplify further...

\begin{align}
  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

\begin{align}
  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.

\begin{align}
  \dot{X}_{nm} =
  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
   \text{Ln}(t)^2}\right)}{2
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
   \text{Ln}(t)^2}}} - \\
  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
   \text{Ln}(t)^3}\\
  &-\frac{\text{Ls}
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
       \text{Ln}(t)^2}}}\\
  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
   \text{Ln}(t)^2}
\end{align}

This is becoming really ugly! I think I want to try another thing. Tomorrow I'll try and implement a different angle scheme and see if it works out easier...this is not tenable. The advantage to this scheme is that it avoids ambiguity, but it is also really really complicated. And even this model has ambiguity in that certain angles could have positive/negative values, so the C code will have to have memory and guess which value is correct. So I think it would be good to choose a simpler ambiguous model and code in ambiguity-resolution to the C code.\\

@@
